Handwriting Recognition

### 2017-12-05 Report/paper.tex
Visualisation code for experiments

\usepackage{times}
\usepackage{graphicx} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{icml2016} 
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{qtree}

@@

\subsubsection{Preliminary steps}
\label{sec:preproc}
We make use of 2 types of preprocessing steps: normalization of the data (\ref{par:norm}) and augmentation of the data (\ref{par:aug}). Normalization of data adjusts the original data and data augmentation takes the data and uses augmentation techniques to create variations of the original data.

@@

\subsubsection{Vocabularium}
\label{sec:voc}
The neural network does not only produce which character is recognised, but rather a list of probabilities indicating the chance of an image to be a certain character. We can use all of this information in this postprocessing step instead of throwing that information away and naively returning the most likely character as the actual character. 
We make a tree, as shown in \ref{fig:wordtree}, where every node is a tuple with a word (sequence of characters) and a probability (likeliness of that word based on the probabilities of individual characters). The probability is calculated as a product of probability for each character.  
\begin{figure}
        %\Tree[.Y [.e [.s] [.5] [.l [.s] [.5]]]]
        %\Tree[.Y]
        \Tree [.{(Y, 0.9)} 
        [.{(Ye , 0.72)} {(Yes, 0.432)} {(Ye5 , 0.288)} ] 
        [.{(Yl , 0.18)} {(Yls, 0.108)} {(Yl5 , 0.072)} ]
            ] 
        \Tree [.{(T, 0.1)} 
        [.{(Te , 0.08)} {(Tes, 0.048)} {(Te5 , 0.032)} ] 
        [.{(Tl , 0.02)} {(Tls, 0.012)} {(Tl5 , 0.008)} ]
            ] 
\label{fig:wordtree} 
\caption{A list of the trees for the word 'Yes' with branching factor 2. The characters have the following probabilities: $P(Y)=0.9, P(T)=0.1, P(e)=0.8, P(l)=0.2, P(s)=0.6, P(5)=0.4$. Other characters have probabilities which are neglible.}
\end{figure} 
\subsubsection{Language model}
\label{sec:lm}
\section{Experiments and results}
\label{sec:expres}
\section{Conclusion}

>>>>

\usepackage{times}
\usepackage{graphicx} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{icml2016} 
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{qtree}
\usepackage{listings}
\usepackage{titlesec}

@@

\subsubsection{Preliminary steps}
\label{sec:preproc}
We make use of 2 types of preprocessing steps: normalization of the data and augmentation of the data. Normalization of data adjusts the original data and data augmentation takes the data and uses augmentation techniques to create variations of the original data.

@@

\subsubsection{Vocabularium}
\label{sec:voc}
The neural network does not only produce which character is recognised, but rather a list of probabilities indicating the chance of an image to be a certain character. We can use all of this information in this postprocessing step instead of throwing that information away and naively returning the most likely character as the actual character. 
\begin{figure}
        \Tree [.{(Y, 0.9)} 
        [.{(Ye , 0.72)} {(Yes, 0.432)} {(Ye5 , 0.288)} ] 
        [.{(Yl , 0.18)} {(Yls, 0.108)} {(Yl5 , 0.072)} ]
            ] 
        \Tree [.{(T, 0.1)} 
        [.{(Te , 0.08)} {(Tes, 0.048)} {(Te5 , 0.032)} ] 
        [.{(Tl , 0.02)} {(Tls, 0.012)} {(Tl5 , 0.008)} ]
            ] 
\caption{A list of the trees for the word 'Yes' with branching factor 2. The characters have the following probabilities: $P(Y)=0.9, P(T)=0.1, P(e)=0.8, P(l)=0.2, P(s)=0.6, P(5)=0.4$. Other characters have probabilities which are neglible.}
\label{fig:wordtree} 
\end{figure} 
We make a tree, as shown in figure \ref{fig:wordtree}, where every node is a tuple with a word (sequence of characters) and a probability (likeliness of that word based on the probabilities of individual characters). The probability is calculated as a product of probability for each character. In order to keep the complexity low we only consider the 3 most probable characters. This will be the branching factor of every tree. There's a tree for every possible starting character. 
Now we have a list of words and their probabilities (every leaf). We can calculate the closest matches in the dictionary for each word. For this purpose we use the function \lstinline{get_close_matches} from the python library difflib. We use function to find close matches in the English dictionary and their corresponding score. We multiply this score with our previously calculated probability. This leaves us with a list of correct English words and a score for every word. If we only want to convert the image of one word into text, we can just return the word with the highest score. 
\subsubsection{Language model}
\label{sec:lm}
Besides checking the syntax of words, we can also look at the context. This is were language models are useful. We can check the previous words and calculate the likeness of a word to be the next word. N-gram models are used to calculate probabilities given n previous words. 
% TODO: More elaborate explanation of n-gram models. I need the internetz for this. 
In order for these n-gram models to be useful. We need a dataset. Google has published n-gram corpora to the public and is free to use. Querying these datasets takes several minutes, and this needs to happen for every word. Instead we use a python library phrasefinder to make online queries to these corpora. This greatly increases speed but has the disadvantage of requiring internet connection. 
Now we can make queries such as "I like dogs / cats / sheep". Using the Google corpora probabilities are calculated with n-gram models for each of the 3 words. Now we have a probability for every word based on the context. 
Combining the results with the probabilities calculated in section \ref{sec:voc}, we can 
calculate a new score. The word with the highest score is accepted as written word. By iterating over all of the words, we now have converted the image with written text into text. In the next section we will
further discuss the results of these techniques and some experiments to check the performance and impact of optimizations. 
\section{Experiments and results}
\label{sec:expres}
\section{Conclusion}
